Quantum H theorem, variational entropy, and relaxation processes

### 2021-01-19 tex/disscussion.tex
Rewording: up to sec. 3.2.1
partial commit, rew: sec5

\section{Discussions and remarks}\label{sec:disscussion}

@@

Besides, we find an expression for the entropy density (\ref{H-entropy}). This expression will be useful to describe quantum gases in terms of entropy.\\

>>>>

\color{black}
\section{Discussions and remarks}\label{sec:disscussion}

Traditionally, the proof of the classical $H$-theorem involves assuming that the
distribution function is spatially homogeneous, and the proof starts with
considering particular systems that are out of equilibrium, but in such a manner
that their distribution functions are still homogeneous. This out-of-equilibrium systems
are conceived considering the micro-states of the system, and the $H$-theorem determines
the microscopic evolution of the system towards a state with the most-probable distribution function,
given a thermodynamic state. 
This approach does not cover systems with spatial inhomogeneities.
To address this issue, we
proposed a framework that may be useful to describe the time-evolution of systems
initially out of equilibrium and spatially non-homogeneous. For this, we divided the
system into small cells, so as to conceive a system wherein the local equilibrium
hypothesis is valid for each cell and the global system is not homogeneous. Systems
that satisfy the previous conditions will evolve towards global equilibrium, and the evolution is
determined by the relations $d\mathcal{H}'/dt\leq0$, Eq.~(\ref{eq:cHdef}),
and $d\mathcal{H}/dt\leq0$, Eq.~(\ref{eq:qHdef}), for classical and quantum gases, respectively.

The $H$-functionals $\mathcal{H}'$ and $\mathcal{H}$ correctly recover the most-probable distribution
functions both in out-of-equilibrium states (locally) and when the system is in the global
equilibrium state. This enables the use of all the machinery of thermodynamics, including the
proper definition of state variables for each cell and

\color{blue}

@@

Besides, we find an expression for the entropy density (\ref{eq:varEntropyDef}). This expression will be useful to describe quantum gases in terms of entropy.\\
